Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-24 paper/ms.tex
nb: add interact_template
update ms

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the
number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, and the slowest five span
27\,hr$<$$P$$<$38\,hr.
Regarding likely astrometric or visual binaries,
\ngoodhighruwe/\ngoods\ high-quality CQVs have a Gaia DR3 RUWE$>$2;
\nmaybehighruwe/\nmaybes\ of the ambiguous sample share this
characteristic.

@@

It is amusing that in identifying the two ambiguous CQV sources in
Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
TIC~57830249), we were prompted to reconsider our light curve-based
labeling, to
ultimately conclude that these sources are dippers.  This episode
suggests that there could be overlap between CQVs and dippers.  It is also worth emphasizing that our labeling of
e.g.~TIC~57830249 was based on a single sector of TESS data
(Sector~36) when its behavior is relatively periodic and it showed
dip depths of a few percent.  However in other TESS sectors
(e.g. Sector~10), this source looks completely different, varying in
apparent flux by a factor of two, with hardly any discernible
periodicity at all.

@@

>>>>

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ CQVs.  The objects are sorted first in order of the
number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, and the slowest five span
27\,hr$<$$P$$<$38\,hr.
Regarding likely astrometric or visual binaries,
\ngoodhighruwe/\ngoods\ high-quality CQVs have a Gaia DR3 RUWE$>$2;
\nmaybehighruwe/\nmaybes\ of the ambiguous sample share this
characteristic.
% This is consistent with Rappaport2014's visual binary fraction determined from
% 30/100 rapidly rotating Kepler stars having multiple periodicities

@@

It is amusing that in identifying the two ambiguous CQVs in
Section~\ref{subsec:irexcess} with outlying SEDs (TICs~193136669 and
TIC~57830249), we were prompted to reconsider our light curve-based
labeling, to
ultimately conclude that these sources are dippers.  This episode
suggests that there could be overlap between CQVs and dippers.  It is also worth emphasizing that our labeling of
e.g.~TIC~57830249 was based on a single sector of TESS data
(Sector~36) when its behavior is relatively periodic and it showed
dip depths of a few percent.  However in other TESS sectors
(e.g. Sector~10), this source looks completely different, varying in
apparent flux by a factor of two, with hardly any discernible
periodicity at all.

@@

\subsection{Is it inflow or outflow?}

The B-star analogy is an outflow.
Debris disks are an inflow.
It seems to match the B-star analogy.
